State Results

### 2023-07-10 reports/county_figures.Rmd
update figures

###########################################################################
# plot relationship between ratio of estimated cases to observed 
# against testing rate 
###########################################################################
county %>%
  ggplot(aes(x=total/population, y = exp_cases_median/positive, color=population)) +
  geom_point(alpha=.03, size=.9) +
  geom_linerange(aes(ymin = exp_cases_lb/positive,
                     ymax=exp_cases_ub/positive ),
                 alpha=.03) +
  facet_wrap(~vlabel,
               labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  theme_c(axis.text.x = element_text(size =9),
          axis.title = element_text(size=16) ) +
  theme(strip.text.x = element_text(size=11, color="white")) +
  scale_y_continuous(n.breaks=10) +
  geom_hline(yintercept=1, linetype=2,color="darkred", alpha=.8, linewidth=.5) +
  labs(y = "Ratio of Estimated Infections to Observed Infections",
       x = "Testing Rate",
       subtitle = "All Time Intervals and All States",
       title = "Relationship Between Testing Rate and\nRatio of Estimated Infections to Observed Infections")+
  scale_x_continuous( n.breaks=4, limits=c(lb,.3))

@@

county_coverage <- county_covidestim %>% get_coverage(geo_scale="County")
saveRDS(county_coverage, here("figures/table_data/county_coverage.RDS"))

state_coverage <- state_covidestim %>% get_coverage(geo_scale="State")
saveRDS(state_coverage, here("figures/table_data/state_coverage.RDS"))

@@

\@ref(table:coverage) is

>>>>

###########################################################################
# plot relationship between ratio of estimated cases to observed 
# against testing rate -- colored by county 
###########################################################################
county %>%
  ggplot(aes(x=total/population, y = exp_cases_median/positive, color=name)) +
  geom_point(alpha=.03, size=.9) +
  geom_linerange(aes(ymin = exp_cases_lb/positive,
                     ymax=exp_cases_ub/positive ),
                 alpha=.03) +
  facet_wrap(~vlabel,
               labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  theme_c(axis.text.x = element_text(size =9),
          axis.title = element_text(size=16) ) +
  theme(strip.text.x = element_text(size=11, color="white")) +
  scale_y_continuous(n.breaks=10) +
  geom_hline(yintercept=1, linetype=2,color="darkred", alpha=.8, linewidth=.5) +
  labs(y = "Ratio of Estimated Infections to Observed Infections",
       x = "Testing Rate",
       subtitle = "All Time Intervals and All States",
       title = "Relationship Between Testing Rate and\nRatio of Estimated Infections to Observed Infections")+
  scale_x_continuous( n.breaks=4, limits=c(lb,.3))

```{r, fig.height=12}

###########################################################################
# plot relationship between ratio of estimated cases to observed 
# against testing rate  -- faceted by county 
###########################################################################
county %>%
  ggplot(aes(x=total/population, y = exp_cases_median/positive)) +
  geom_point(alpha=.03, size=.9) +
  geom_linerange(aes(ymin = exp_cases_lb/positive,
                     ymax=exp_cases_ub/positive ),
                 alpha=.03) +
  facet_grid(name~vlabel,
               labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  theme_c(axis.text.x = element_text(size =9),
          axis.title = element_text(size=16) ) +
  theme(strip.text.x = element_text(size=11, color="white")) +
  scale_y_continuous(n.breaks=10) +
  geom_hline(yintercept=1, linetype=2,color="darkred", alpha=.8, linewidth=.5) +
  labs(y = "Ratio of Estimated Infections to Observed Infections",
       x = "Testing Rate",
       subtitle = "All Time Intervals and All States",
       title = "Relationship Between Testing Rate and\nRatio of Estimated Infections to Observed Infections")+
  scale_x_continuous( n.breaks=4, limits=c(lb-.02,.3))

@@

county_coverage <- county_covidestim %>% get_coverage(geo_scale="County Level (in Massachusetts)")
saveRDS(county_coverage, here("figures/table_data/county_coverage.RDS"))

state_coverage <- state_covidestim %>% get_coverage(geo_scale="State Level")
saveRDS(state_coverage, here("figures/table_data/state_coverage.RDS"))

@@

### 2023-07-10 reports/priors.Rmd
update figures

@@

>>>>

tibble(x = seq(0, 1, length = 10^(5)),
       y = with(prior_params, beta_density(x,
                                     mean = .55,
                                     sd = .12,
                                     bounds = NA))) %>%
   ggplot(aes(x=x, y = y)) +
  geom_line(alpha = .8) + 
  geom_ribbon(aes(x=x,ymin=0,ymax=y),
              fill="black",
              alpha=.6) +
  theme_c(legend.text=element_text(size = 10)) +
  viridis::scale_fill_viridis(discrete=TRUE,
                             option = "rocket", begin=.3,end=.8) +
  labs(x = "Value",
       y = "Probability Density", 
       title = latex2exp::TeX("Definition of Prior for $P(S_0|test_+,untested)$"),
       fill ='',
       subtitle = paste0("Mean: ", .55,
                         ", SD: ", .12)) +
  scale_x_continuous(n.breaks=11)

tibble(samp =sample_beta_density(1e4, mean = .55,
                                     sd = .12,
                                     bounds = NA))

qbeta(.025, shape1= get_beta_params( mu = .55,
                                     sd = .12)$a,
      shape2= get_beta_params( mu = .55,
                                     sd = .12)$b
      )

qbeta(.975, shape1= get_beta_params( mu = .55,
                                     sd = .12)$a,
      shape2= get_beta_params( mu = .55,
                                     sd = .12)$b
      )

@@

# Bayesian Melding

library(patchwork)
library(truncdist)

source(here('R/04-melding.R'))

params <- prior_params
params$beta_shape1 <- beta_shape[1]
params$beta_shape2 <- beta_shape[2]
params$s_untested_shape1 <- s_untested_shape[1]
params$s_untested_shape2 <- s_untested_shape[2]
params$direct_params <- TRUE
# 
# prior_params <- list(
#     alpha_mean = .95,
#     alpha_sd = 0.08,
#     alpha_bounds = NA,
#    # alpha_bounds = c(.8,1),
#     beta_mean = .15,
#     beta_sd =.09,
#     beta_bounds = NA,
#   #  beta_bounds = c(0.002, 0.4),
#     s_untested_mean = .03,
#     s_untested_sd = .0225,
#   #  s_untested_bounds = c(0.0018, Inf),
#     s_untested_bounds = NA,
#     p_s0_pos_mean = .4,
#     p_s0_pos_sd = .1225,
#  #  p_s0_pos_bounds = NA,
#     p_s0_pos_bounds = c(.25, .7),
#     pre_nsamp = 1e4,
#     post_nsamp = 1e4)

melded <- do.call(get_melded, prior_params)

theta_wide <- with(prior_params,  
 theta <- tibble(x= seq(0,1.4, length = 200),
                 alpha = gamma_density(x,
                                       mean = alpha_mean,
                                       sd = alpha_sd,
                                       bounds = alpha_bounds),
                    # beta= beta_density(x,
                    #                           mean = beta_mean,
                    #                           sd = beta_sd,
                    #                           bounds = beta_bounds),
                    # P_S_untested = beta_density(x,
                    #                             mean = s_untested_mean,
                    #                             sd = s_untested_sd,
                    #                             bounds = s_untested_bounds),
                 P_S0_pos = beta_density(x,
                                         mean = p_s0_pos_mean,
                                         sd = p_s0_pos_sd,
                                         bounds = p_s0_pos_bounds)
                 )) %>%
  mutate(beta = dbeta(x, shape1= beta_shape[1], shape2=beta_shape[2]),
         P_S_untested = dbeta(x, shape1=s_untested_shape[1],
                              shape2=s_untested_shape[2] ))

theta_samp<- with(prior_params,  
 theta <- tibble(alpha = sample_gamma_density(pre_nsamp,
                                                mean = alpha_mean,
                                                sd = alpha_sd,
                                                bounds = alpha_bounds),
                    beta= rbeta(pre_nsamp,
                                shape1= beta_shape[1], 
                                shape2=beta_shape[2]),
                    P_S_untested = rbeta(pre_nsamp,
                                         shape1=s_untested_shape[1],
                                         shape2=s_untested_shape[2])) %>%
        mutate(phi_induced = est_P_A_testpos(P_S_untested = P_S_untested,
                                             alpha = alpha,
                                             beta=beta))) %>%
  select(phi_induced)

theta <- theta_wide %>% 
  pivot_longer(-c(x)) %>%
    mutate(name = case_when(
      name == "alpha" ~"$\\alpha$",
      name == "beta" ~"$\\beta$",
      name == "phi_induced" ~ "$M(\\theta) = Pr(S_0|test+,untested)$",
      name == "P_S_untested" ~ "$Pr(S_1|untested)$",
      name == "P_S0_pos" ~ "$Pr(S_0|test+,untested)$")
    ) %>%
    mutate(name = factor(name,
                         levels = c(
                           "$\\alpha$",
                           "$\\beta$",
                           "$Pr(S_1|untested)$",
                           "$Pr(S_0|test+,untested)$",
                           "$M(\\theta) = Pr(S_0|test+,untested)$")))

```{r, fig.width=9,fig.height=9}

melded_long <- reformat_melded(melded$post_melding,
                               melded$pre_melding,
                               pre_nsamp = prior_params$pre_nsamp,
                              p_s0_pos_mean = prior_params$p_s0_pos_mean,
                              p_s0_pos_sd = prior_params$p_s0_pos_sd,
                              p_s0_pos_bounds = c(.3,.7)) %>%
  filter(type=="After Melding") %>%
  mutate(name = gsub("$P(S_1|untested)$",
                     "$Pr(S_1|untested)$", name,fixed=TRUE),
         name = gsub("$P(S_0|test+,untested)$",
                     "$Pr(S_0|test+,untested)$", name, fixed=TRUE)) %>%
    mutate(name = factor(name,
                         levels = c(
                           "$\\alpha$",
                           "$\\beta$",
                           "$Pr(S_1|untested)$",
                           "$Pr(S_0|test+,untested)$")))

plt1 <- theta %>% 
  filter(name != "$M(\\theta) = Pr(S_0|test+,untested)$" & name !=  "$Pr(S_0|test+,untested)$") %>%
  ggplot() +
  geom_ribbon(aes(x=x, ymin=0, ymax= value, fill='Before Melding'),alpha=.7, color=NA)+
  geom_density(aes(x=value, fill = 'After Melding'), 
               color=NA,
               data = melded_long[melded_long$name !=
                                    "$Pr(S_0|test+,untested)$",]) +
  facet_wrap(~name,
             labeller=  as_labeller(TeX, default = label_parsed),
             ncol = 3, scales="free_y") +
  theme_c()+
  theme(legend.position="right",
          axis.text.x=element_text(size=6),
          axis.title.x=element_text(size=12),
          axis.title.y=element_text(size=12)) +
  theme(legend.position="none") +
  scale_x_continuous(n.breaks=5) +
  labs(x="Value")+
scale_fill_manual(values = c("Before Melding"= "#5670BF", "Induced" = "#B28542",
                                 "After Melding" = "#418F6A"))

theta_samp <- theta_samp %>% mutate(name ="$Pr(S_0|test+,untested)$" )

plt2 <- theta %>% 
  filter(name==  "$Pr(S_0|test+,untested)$") %>%
  ggplot() +
  geom_ribbon(aes(x=x, ymin=0, ymax= value, fill='Before Melding'),alpha=.7)+
  geom_density(aes(x=value, fill = 'After Melding'),
               alpha=.7,color=NA,
               data = melded_long[melded_long$name ==
                                    "$Pr(S_0|test+,untested)$",]) +
    geom_density(aes(x= phi_induced, fill="Induced"), 
                 color = NA,
                 data = theta_samp,
                 alpha =.7) +
  facet_wrap(~name,
             labeller=  as_labeller(TeX, default = label_parsed),
             ncol = 3, scales="free_y") +
  theme_c() +
  theme(legend.position="right",
          axis.text.x=element_text(size=6),
          axis.title.x=element_text(size=12),
          axis.title.y=element_text(size=12))+
  scale_x_continuous(n.breaks=5, limits =c(0,1)) +
  labs(x="Value",
       fill = "")+
    scale_fill_manual(values = c("Before Melding"= "#5670BF", "Induced" = "#B28542",
                                 "After Melding" = "#418F6A"))

plt1 / plt2

ggsave(here('figures/melding-priors.pdf'))

### 2023-07-10 reports/state_figures.Rmd
update figures

>>>>

```{r,eval=FALSE, include=FALSE}

dates <- readRDS(here("data/data_raw/date_to_biweek.RDS"))

v7_1 <- tar_read(ma_v1, store="_targets_7_08") %>%
  mutate(targets_version="1")

v7_2 <- tar_read(ma_v1, store="_targets") %>%
  mutate(targets_version="2")

v7_1 <- tar_read(state_v1, store="_targets_7_08") %>%
  mutate(targets_version="1")

v7_2 <- tar_read(state_v1, store="_targets") %>%
  mutate(targets_version="2")

v7_1 %>%
  bind_rows(v7_2) %>%
  filter(fips %in% sample(unique(v7_1$fips),5)) %>%
  left_join(dates,relationship = "many-to-many" ) %>%
  ggplot(aes(x=date, 
             ymin = exp_cases_lb,
             ymax=exp_cases_ub,
             fill = targets_version)) +
  geom_ribbon(alpha=.6) +
  facet_wrap(~fips,scales="free")

v7_1 %>%
  bind_rows(v7_2) %>%
  select(fips, exp_cases_median, biweek, targets_version) %>%
  pivot_wider(names_from=targets_version,
              values_from = exp_cases_median,
              names_prefix="exp_cases_targets_v") %>%
  mutate(diff =exp_cases_targets_v1 - exp_cases_targets_v2) %>% 
  summarize(diff =mean(diff))
